---
title: "Enron_file"
output: html_notebook
---



```{r}
library(readr)
enron <- read_csv("enron_pickle.csv")
```

summarize the data

```{r}
summary(enron)
```
remove text values from table (email address), convert boolean to class, 
and remove nans


```{r}
enron_reduced = subset(enron, select = - c (email_address))
enron_reduced$poi <- as.integer(enron_reduced_nobool$poi == "True")
```

count number of NAs

```{r}
sum(is.na(enron_reduced))
```
replace NAs with 0

```{r}
enron_reduced[is.na(enron_reduced)] <- 0
```

export enron data set with replaced Nan values to new csv

```{r}
write.csv( file= "enron_pickle_nona.csv", x =enron_reduced)
```

write new csv file which converts boolean to integer value

```{r}
enron_reduced_nobool <- enron_reduced

```

make new data set with only the poi values for feature selection exercise

```{r}
enron_poi <- enron_reduced = subset(enron, select = c(poi ))
```


```{r}
write.csv( file= "enron_pickle_nona_nobool.csv", x =enron_reduced_nobool)
```


determine correlation table
```{r, fig.width=2}
cor(enron_reduced)
```


getting all the column names for feature selection in the python file poi_id.py

```{r}
colnames(enron)
```

